Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-18 bbbq_article.tex
First step towards a proper discussion

[GVDB: 
  Discussion section needs some work, 
  as here interpretation of the results needs to be given. 
  What is the consequence of the findings? Why is it important.

  Now it is just a list of potential reasons why the results might be flawed. 
  While this is in principle OK, 
  it is also nitpicking as some things affect only a limited number of 
  proteins (like selenoproteins) 
  or you’d expect changes in the other direction (wrong prediction of TMHs for bacteria).

  So offer interpretations. 
  The second part of the introduction would fit here well. I can also help with this.
]

@@

@@

[RJCB: this paragraph I ruthlessly moved
from introduction to here, as was suggested by GVDB]

In general, on would hope that evolutionary selection results in
an immune system that as most attentive for loci that are
essential for a virus, as these will be most conserved.
In SARS-CoV-2, for example, there is preliminary evidence that the strongest
selection pressure is upon residues that changes its 
virulence (\cite{velazquez2020positive}).
These loci, however, only account for a small part of a pathogen's proteome.
Additionally, these essential parts differ widely between pathogens.
Because of this scarcity and variance in targets, 
one can imagine that the human immune system 
is not tailored to detect these sites, 
 as hinted by upon by the aforementioned influenza study.

@@

[RJCB: this paragraph I ruthlessly moved
from introduction to here, as was suggested by GVDB]

TMHs, on the other hand, also have their function constraints, 
yet can occur multiple time a pathogen's proteome.
One can safely assume a pathogen's proteome contains multiple TMHs.
Therefore, it may be beneficial for the host
if its immune system would be more attentive towards TMHs.
And maybe this has already happened: MHC-I already detects hydrophobic
peptides. This feature, however, may also be caused by selection
to detect hydrophobic regions in the soluble proteins of pathogens.
It is unknown, when focusing on TMHs only, if a signal of selection
can be detected.

\subsection{Evolutionary conservation}

[GVDB: 
  This might be relevant, but you need to explain why it is relevant. 
  Thus compare your findings with previous efforts 
  to look at conservation of TMHs
]
% \paragraph{synonymous mutations}
%
In our evolutionary experiment, 
we removed variations that were synonymous mutations (i.e.
resulted in the same amino acid, from a different genetic code) 
from our analysis.
There is evidence, however, that these synonymous mutations
do have an effect and may even be evolutionary selected 
for (\cite{hunt2009silent}).
As the possible effect of synonymous mutations is ignored by our
topology prediction software, we do so as well.

The NCBI dbSNP database contains millions of SNPs.
As the NCBI API constrains its users to three calls per second,
we had to limited the extent of our analysis.

[RJCB: this paragraph I ruthlessly moved
from introduction to here, as was suggested by GVDB]
We concluded that the
epitopes that MHC-I presents are [as/not as] likely 
to be derived from TMH within either a human host and its bacterial pathogen.
Because a bacterium does not infect a cell, thus its peptides
will not be presented by MHC-I, this result is [unexpected/expected]

[RJCB: this paragraph I ruthlessly moved
from introduction to here, as was suggested by GVDB]
We aimed our evolutionary experiment at TMHs, because these can
be predicted well from a protein structure,
are common structures and are present in all pathogens. 
We could have done the same experiment on beta-turn,
as also these can be predicted well (\cite{petersen2010netturnp}),
are common structures and are present in all pathogens.

[RJCB: this paragraph I ruthlessly moved
from introduction to here, as was suggested by GVDB]
The human immune system and human pathogen are in an evolutionary
arms race: our immune systems is selected for the detection
of pathogens, whereas pathogens are selected to avoid detection.
From a pathogen's point of view, however, this struggle 
is of only minor importance:
in seasonal influenza, for example, the selection pressure
exerted by the immune system was only limited (\cite{han2019individual}).

% \paragraph{Interesting haplotype for SARS-CoV-2}

It is known that an individual's haplotype
influences the dynamics of a pathogen.
For example, in the fast-mutating HIV virus, 
HLA haplotypes that are likelier to induce a specific T-cell response
for the Gag protein slow down the disease's 
progression \cite{eccleston2017host}.
The bioinformatics pipeline developed in this
study may be interesting to make in silico
predictions of a SARS-CoV-2 infection.
The most prominent example is the (MHC-I)
haplotype HLA-A*24:02,
which is predicted to present four times as much epitopes derived 
from SARS-CoV-2 TMHs than expected by chance.
This may help the immune system to detect a SARS-CoV-2 infection earlier,
and change the infection's dynamics.

@@

>>>>

[GVDB: 
  Discussion section needs some work, 
  as here interpretation of the results needs to be given. 
  What is the consequence of the findings? Why is it important. 
]

@@

The NCBI dbSNP database contains millions of SNPs.
As the NCBI API constrains its users to three calls per second
to assure fair use, we had to limit the extent of our analysis.
We assume we have taken a representative sample, but only
an analysis using the full NCBI database can confirm this.

@@

In general, on would hope that evolutionary selection results in
an immune system that as most attentive for loci that are
essential for a virus, as these will be most conserved.
In SARS-CoV-2, for example, there is preliminary evidence that the strongest
selection pressure is upon residues that changes its 
virulence (\cite{velazquez2020positive}).
These loci, however, only account for a small part of a pathogen's proteome.
Additionally, these essential parts differ widely between pathogens.
Because of this scarcity and variance in targets, 
one can imagine that the human immune system 
is not tailored to detect these sites, 
as hinted by upon by a extensive study on influenza (\cite{han2019individual}),
where it was found that the selection pressure
exerted by the immune system was only limited.

@@

TMHs, on the other hand, also have their function constraints, 
yet can occur multiple time a pathogen's proteome.
One can safely assume a pathogen's proteome contains multiple TMHs.
Therefore, it may be beneficial for the host
if its immune system would be more attentive towards TMHs.
And maybe this has already happened: MHC-I already detects hydrophobic
peptides. This feature, however, may also be caused by selection
to detect hydrophobic regions in the soluble proteins of pathogens.
It is unknown, when focusing on TMHs only, if a signal of selection
can be detected.
We speculate that the human immune system is more attentive 
towards TMHs, as it is a general structure, that is evolutionarily conserved.

We aimed our evolutionary experiment at TMHs, because these can
be predicted well from a protein structure,
are common structures and are present in all pathogens. 
We could have done the same experiment on beta-turn,
as also these can be predicted well (\cite{petersen2010netturnp}),
are common structures and are present in all pathogens.
We speculate that the human immune system may also be more attentive 
towards beta turns for this reason.

[GVDB: 
  Also compare your findings with previous efforts 
  to look at conservation of TMHs
]

@@

% \paragraph{synonymous mutations}
%
In our evolutionary experiment, 
we removed variations that were synonymous mutations (i.e.
resulted in the same amino acid, from a different genetic code) 
from our analysis.
There is evidence, however, that these synonymous mutations
do have an effect and may even be evolutionary selected 
for (\cite{hunt2009silent}).
As the possible effect of synonymous mutations is ignored by our
topology prediction software, we do so as well.
